Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-05-27 02_paper/02_study/paper_methods.tex
update method section

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\hypertarget{eye-tracking-equipment}{%
\subsubsection{Eye-Tracking equipment}\label{eye-tracking-equipment}}

During the unit, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (\url{https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}). The system consisted of a wearable head unit and a recording unit. As shown in Figure \ref{fig:tobiiglasses2}, the head unit was a measuring device with different sensors. A high-definition scene camera captured a full HD video of the teacher's field of vision. An integrated microphone recorded the surrounding sounds. Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capure the tacher's gaze point as shown in Figure \ref{fig:teachergazepoint}. The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second. The scene camera had a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).

@@

{\centering \includegraphics{./pictures/teachergazepoint}

@@

\caption{Teacher's Gaze Point}\label{fig:teachergazepoint}
\end{figure}

\hypertarget{video-and-audio-recording-equipment}{%
\subsubsection{Video and Audio recording equipment}\label{video-and-audio-recording-equipment}}

@@

\hypertarget{questionnaire}{%
\subsubsection{Questionnaire}\label{questionnaire}}

After each micro-teaching-unit, the students answered items on teaching quality using a validated questionnaire (Helmke et al., 2014) and scales on the teacher's presence behavior. In addition, participants were asked to give a self-assessment on classroom management by completing the questionnaire after each micro-teaching-unit. The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).

@@

@@

In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and August 2022.

@@

The subjects were informed in detail about the procedure and aim of the study before the survey. For the data collection, student teachers and experienced teachers were asked to prepare micro-teaching-unit of 15 minutes. The subjects taught the micro-teaching-unit to a fictitious class consisting of three student assistants who simulated typical classroom events during the lesson. A mobile eye-tracker recorded the teachers' gaze behavior and audio data of the lesson. All other sounds and voices were also recorded using audio recorders. In addition, the test persons were given a smartwatch to record the number of steps they took and their pulse rate. To record facial expressions, gestures and movements, four mobile cameras were installed to record the fictitious classroom from all perspectives (see figures 5-8). After the lesson, the teacher conducted a letter search in the room. For this, four letters had to be found in order and read aloud. This served as a control condition for the speed of the subjects' perceptual ability.
of the test persons. After the end of the teaching sequence, the class and the teacher
After the end of the teaching sequence, the class and the teacher filled out a questionnaire focusing on evidence-based methods of teaching diagnostics (EMU) in order to collect data on self-assessment and assessment by others.

In the second part of the survey, the investigator conducted a Stimulated-
Recall Interview (SRI) with the respondents. In this interview, the recorded video of the lesson was watched in its entirety and commented on by the teacher while thinking aloud. Finally, the test persons answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Experimental stimuli are freely available in the following online repository: \url{https://github.com/}\ldots{} .

\hypertarget{eye-tracking-data}{%
\subsubsection{Eye-Tracking data}\label{eye-tracking-data}}

During the lesson, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (\url{https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}). The system consisted of a wearable head unit and a recording unit. As shown in Figure \ref{fig:tobiiglasses2}, the head unit was a measuring device with different sensors. A high-definition scene camera captured a full HD video of the teacher's field of vision. An integrated microphone recorded the surrounding sounds. Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \ref{fig:teachersgaze}. The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second. The scene camera had a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).

@@

{\centering \includegraphics{./pictures/teachersgaze}

@@

\caption{Teacher's Gaze Point}\label{fig:teachersgaze}
\end{figure}

\hypertarget{behavioral-data}{%
\subsubsection{Behavioral data}\label{behavioral-data}}

@@

\hypertarget{questionnaire-data}{%
\subsubsection{Questionnaire data}\label{questionnaire-data}}

After each micro-teaching-unit, the three actors answered items on teaching quality using a validated questionnaire (Helmke et al., 2014) and self developed scales on the teacher's presence behavior derived from the research literature. In addition, subjects were asked to give a self-assessment on classroom management by completing the same questionnaire after each micro-teaching-unit. The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).

@@

\hypertarget{verbal-data}{%
\subsubsection{Verbal data}\label{verbal-data}}

In addition to the eye-tracking, questionnaire and behavioral data, verbal data was also collected in the form of a Stimulated Recall Interview.

\ref{fig:sri}

{\centering \includegraphics{./pictures/sri}

\caption{Subject and experimenter during the Stimulated Recall Interview}\label{fig:sri}
\end{figure}

@@

@@

In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and \ldots{} 2022.

Before the data collection, each subject received a personal digital meeting with the experimenter to go over the study procedure and to arrange a date for the data collection. During the digital meeting, the subjects were asked to prepare a 15-minute lesson in a subject and grade of their choice for the data collection.

On the day of a data collection, the first step was to set up the study room at the University of Leipzig. For this, all the appropriate technical equipment was charged and installed in the room (see set up plan {[}REFERENZ EINFÜGEN{]}). Next, all four cameras and the audio recorder were synced via Timecode System.

After the subject arrived, a smart watch was put on to measure the heart rate during the session and to get a pretest time at least 15min before the session started. In addition to the experimenter and the subject, three student assistants from the working group always took part in the data collection, as they represented the class.

After the welcome, the subject was again briefed about the study. It was explicitly pointed out that the student assistants would act as the class and simulate typical class events during the lesson. The subject was asked in advance to behave as naturally as possible during the entire time. Next, the subjects' written informed consent was obtained and contact details were collected in order to inform all persons participating in the study if a covid infection should occur.

After the introduction, the eye-tracking glasses were adjusted for the subject by inserting contact lenses if necessary and changing the nose pad. To start the eye tracking glasses, the Tobii Glasses must be fitted onto the subject's head via an one-point-calibration. In the calibration process the subject was asked to look at a Calibration Card held in-front of the subject for a few seconds. The experimenter started the recording from Tobii Glasses Controller Software running on a computer.

After starting the eye tracking recording, all other technical devices were also switched on: The four cameras and the audio recorder were controlled via iPad using the BLINK Hup app and could be started simultaneously by synchronization. The ZED camera was started manually on another laptop.

Before the 15-minute lesson, there was a short 10-minute warm-up phase. The phase was divided into two parts and served on the one hand to get the subjects used to the eye-tracking glasses and on the other hand to get used to their class. In the first phase of the warm-up, the game ``name juggling'' was played using two balls. In the game, the subject and the three actors threw two balls at each other and, depending on the color of the ball, called either their own name or that of the target person. After the name juggling, the subjects were supposed to start a conversation. For this, the subject thought of a question for each student and was also asked a question of each student. The content could be anything that interested the participants.

After the warm up phase, the experimenter ensured a manual synchronization of the technique by an acoustic signal in which she clapped her hands loudly twice standing in the middle of the room. After this, another nine-point calibration followed outside the study room in a neighboring room. Before the subject left the room for calibration, the time on the smartwatch was noted, as well as the steps recorded until that point. The subject had to stand at a marked point and look at a board three meters away with nine april tags. The subject was asked to read the nine points aloud in order at a normal speaking speed. This procedure was important to validate the one-point calibration on the one hand and on the other hand to give the subject the feeling of a lesson start, because after this calibration the subject came into the study room to start the 15-minute lesson.

For the micro-teaching lesson, student teachers and experienced teachers were asked to prepare an introduction of 15 minutes which they taught in front of the fictitious class consisting of three student assistants. The actors simulated the nine classroom events during the lesson, derived by research literature. The order of the disruptions as well as the students performing them were fully balanced using Latin Square.

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
verbal disruption
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
agitation
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
lack of eagerness to learn
\end{minipage} \\
\midrule
\endhead
chatting with neighbor & drumming hands & putting head on table \\
whispering with neighbor & clicking pen & looking at phone \\
heckling & snipping with fingers & drawing on a sheet of paper \\
\bottomrule
\end{longtable}

The experimenter used time cards to indicate the time remaining (yellow = one minute remaining; red = time expired).

A mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson. All other sounds and voices were recorded by an audio recorder. To record facial expressions, gestures and movements, four mobile cameras were installed to record the classroom from all perspectives (!!!see figures). After the micro-teaching-unit, the teacher conducted a letter search in the room. For this, four letters had to be found in order and read aloud. This served as a control condition for the speed of the subjects' perceptual ability.

of the test persons. After the end of the teaching sequence, the class and the teacher
After the end of the teaching sequence, the class and the teacher filled out a questionnaire focusing on evidence-based methods of teaching diagnostics (EMU) in order to collect data on self-assessment and assessment by others.

In the second part of the study, the experimenter conducted a Stimulated-Recall Interview (SRI) with the subject. In this interview, the recorded video of the lesson was watched and commented on by the subject while thinking aloud.

Finally, the test persons answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management.
